Output Summary

### 2022-01-11 03-post-process/output-plots.Rmd
Make Rmd plots react to whether these items were toggled on or off

```{r calculate-waic}
summarize_lppd = function(param, LH_type = NULL, origin = NULL, pop = NULL) {
  # calculate total lppd summed across all data sets within a given year
  total_lppd = sapply(observable, function(y) rowSums(post_subset(post, sub_index(param, year = y, LH_type = LH_type, origin = origin, pop = pop), matrix = TRUE)))

@@

@@

```{r calculate-bayesian-pvals}
# function to summarize bayesian p-values within a data source
summarize_bp = function(bp) {
  data.frame(
    "N" = apply(bp, 2, function(x) sum(!is.na(x))),
    "median" = apply(bp, 2, median, na.rm = TRUE),
    "q2.5" = apply(bp, 2, function(x) quantile(x, 0.025, na.rm = TRUE)),
    "q97.5" = apply(bp, 2, function(x) quantile(x, 0.975, na.rm = TRUE)),
    "p_lt_0.05" = apply(bp, 2, function(x) sum(x < 0.05 & !is.na(x))/sum(!is.na(x))),
    "p_gt_0.95" = apply(bp, 2, function(x) sum(x > 0.95 & !is.na(x))/sum(!is.na(x)))
  )
}

@@

```{r bayesian-pvals-table}
# a function to color cells depending on the value
assign_color = function(x) {
  red_pal = colorRampPalette(c("white", "red"))
  blue_pal = colorRampPalette(c("blue", "white"))
  red_cols = red_pal(5)
  blue_cols = blue_pal(5)
  cols = c(blue_cols, red_cols)
  bin_names = levels(cut(rbeta(1e6, 1, 1), breaks = seq(0,1,0.1), include.lowest = TRUE))
  names(cols) = bin_names
  bins = cut(x, breaks = seq(0,1,0.1), include.lowest = TRUE)
  cols_use = cols[as.character(bins)]
  alpha(unname(cols_use), 0.5)
}

@@

>>>>

```{r calculate-waic, eval = model_info$do_lppd}
summarize_lppd = function(param, LH_type = NULL, origin = NULL, pop = NULL) {
  # calculate total lppd summed across all data sets within a given year
  total_lppd = sapply(observable, function(y) rowSums(post_subset(post, sub_index(param, year = y, LH_type = LH_type, origin = origin, pop = pop), matrix = TRUE)))

@@

```{r dont-calculate-waic, eval = !model_info$do_lppd, results='asis'}
cat("_Calculation of log posterior predictive density values needed to calculate WAIC was toggled off when fitting this model, so this output is omitted._")
```

@@

```{r calculate-bayesian-pvals, eval = model_info$do_pp_check}
# function to summarize bayesian p-values within a data source
summarize_bp = function(bp) {
  data.frame(
    "N" = apply(bp, 2, function(x) sum(!is.na(x))),
    "median" = apply(bp, 2, median, na.rm = TRUE),
    "q2.5" = apply(bp, 2, function(x) quantile(x, 0.025, na.rm = TRUE)),
    "q97.5" = apply(bp, 2, function(x) quantile(x, 0.975, na.rm = TRUE)),
    "p_lt_0.05" = apply(bp, 2, function(x) sum(x < 0.05 & !is.na(x))/sum(!is.na(x))),
    "p_gt_0.95" = apply(bp, 2, function(x) sum(x > 0.95 & !is.na(x))/sum(!is.na(x)))
  )
}

@@

```{r bayesian-pvals-table, eval = model_info$do_pp_check}
# a function to color cells depending on the value
assign_color = function(x) {
  red_pal = colorRampPalette(c("white", "red"))
  blue_pal = colorRampPalette(c("blue", "white"))
  red_cols = red_pal(5)
  blue_cols = blue_pal(5)
  cols = c(blue_cols, red_cols)
  bin_names = levels(cut(rbeta(1e6, 1, 1), breaks = seq(0,1,0.1), include.lowest = TRUE))
  names(cols) = bin_names
  bins = cut(x, breaks = seq(0,1,0.1), include.lowest = TRUE)
  cols_use = cols[as.character(bins)]
  alpha(unname(cols_use), 0.5)
}

@@

```{r dont-calculate-bayesian-pvals, eval = !model_info$do_pp_check, results='asis'}
cat("_Generation of simulated data that can be compared to the observed data in terms of model fit was toggled off when fitting this model, so this output is omitted._")
```
